Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-21 article.rnw
Collapse the first two paragraphs of the discussion into one.
They tie together too tightly to be separate paragraphs.
Change a TODO to merely a possible TODO.
Simplify an overly wordy paragraph.

We have shown that it is possible to fit a more parsimonious model of species interactions by grouping the interaction coefficients of species \emph{a posteriori}, and hence reducing the number of free parameters in the model.
Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped.
Which grouping would give the most parsimonious model, however, could not be determined with confidence.

% DBS: Avoid imprecise "this" or "that" as subjects. Always say "This result" or something similar. Also, avoid starting a new paragraph that so strongly forms a continuation of the previous one.
This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.
Perhaps species simply do not group to the same extent in a competitive context.
The results suggest that this is unlikely, as grouping was still likely to increase parsimony.
Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
Perhaps the lack of clarity in the groupings is instead a product of the study system chosen.

@@

% DBS: The paragraph below is a very good example of text that could easily be simplified for clarity without losing important content.
In light of the failure to produce clear groups, perhaps the most curious aspect of the results is the disagreement between the likely coclassifications of species in the groupings of rows and of columns.
This is perhaps not surprising in hindsight, for there is no necessity that species respond to competition in the same manner that they cause it, especially in competition for certain resources such as space (the limiting resource presumed in these data) or light. % DBS: Some definite refs missing here.
Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
My results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
%TODO: Discuss the fact that species were coclassified more in the rows than in the columns.

>>>>

We have shown that it is possible to fit a more parsimonious model of species interactions by grouping the interaction coefficients of species \emph{a posteriori}, and hence reducing the number of free parameters in the model.
Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped.
Which grouping would give the most parsimonious model, however, could not be determined with confidence.
This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.
Perhaps species simply do not group to the same extent in a competitive context.
The results suggest that this is unlikely, as grouping was still likely to increase parsimony.
Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
Perhaps the lack of clarity in the groupings is instead a product of the study system chosen.

@@

While the results could not definitely show the best grouping, it was clear that the appropriate grouping differed for the rows and columns.
That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
This should not be surprising, for it is known that different traits govern species competitive effects than their responses \parencite{goldberg1991competitive}.
Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
My results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
%TODO: Discuss the fact that species were coclassified more in the rows than in the columns?
